Design of Blur Invariant Fiducial for Low Cost Quadcopter

### 2014-02-26 ECCV/paper.tex
1. Added related work about tracking 2. Added simulation details

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{amsmath,amssymb} % define this before the line numbering.
\usepackage{ruler}
\usepackage{color}
\usepackage{url}
\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}

@@

\begin{figure}

 \begin{subfigure}[b]{0.19\textwidth}  
 \centering 
  \includegraphics[width=\linewidth]{pattKanji.pdf}
  \caption{ARToolkit}  
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{ARtag.jpg}
  \caption{ARTag}
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{intersense.jpg}
  \caption{Intersense}  
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{pifiducial.png}
  \caption{Pi-Tag}  
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{newconcentric_01.pdf}
  %\includegraphics[width=0.5\linewidth]{newconcentric_10.pdf}
  \caption{Our Fiducial}  
 \end{subfigure}
 \caption{Various Fiducial Marker Designs}
 \label{fig:previous_work}  
\end{figure}

@@

\subsection{Limitations}
The main hurdle in detection of current fiducials is, the detecton of features;
lines in \cite{ARToolkit02}, corners in \cite{Fiala05} while ellipses in
\cite{Cho:2001}, \cite{Cho97fastcolor}, \cite{runetag11} and \cite{Pitag13}.
Such features are very difficult to correctly detect under significant motion
blur. So, under blur, recognition rate of these fiducials is very low.

Wu et al.\cite{Wu:2011} have developed BLUr-driven Tracker (BLUT) framework for
tracking motion-blurred targets. BLUT framework works well when there is
uniform motion and the position of tracked object does not change drastically in
successive frames. But in our case, due to frequntly dropping of intermediate
frame, this criterion may not be satisfied.

@@

\section{Experimental Validation}
Our system has been tested on the image sequences captured from AR Drone
quadcopter. Each image sequence contains frames containing different fiducial
pattern. Sample output for each fiducial pattern is shown in Fig.
\ref{fig:output0} -- Fig. \ref{fig:output3}.

>>>>

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage[font=small]{caption}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{amsmath,amssymb} % define this before the line numbering.
\usepackage{ruler}
\usepackage{color}
\usepackage{url}
\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}

@@

Our problem may be classified broadly in two areas; fiducial markers and
tracking. So, we will briefly discuss work done in both areas.
\begin{figure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{intersense.jpg}
  Intersense\cite{NaimarkF02}  
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}  
 \centering 
  \includegraphics[width=\linewidth]{pattKanji.pdf}
  ARToolkit\cite{ARToolkit02}  
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{ARtag.jpg}
  ARTag\cite{Fiala05}
 \end{subfigure} 
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{pifiducial.png}
  Pi-Tag\cite{Pitag13}  
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{newconcentric_01.pdf}  
  Our Fiducial  
 \end{subfigure}
 \caption{Various Fiducial Marker Designs}
 \label{fig:previous_work}  
\end{figure}

@@

The main hurdle in detection of current fiducials is, the detecton of features;
lines in \cite{ARToolkit02}, corners in \cite{Fiala05} while ellipses in
\cite{Cho:2001}, \cite{Cho97fastcolor}, \cite{runetag11} and \cite{Pitag13}.
Such features are very difficult to detect accurately under significant motion
blur. So, under blur, recognition rate of these fiducials is very low.

Fiducial detection in video may be considered as tracking problem where tracked
object is fiducial itself. Visual tracking plays an important role in
surveillance, robotics, human computer interaction, and medical
imaging\cite{Yilmaz:2006}. Yilmaz et al.\cite{Yilmaz:2006} have done survey of
various tracking methods. Most tracking methods
( \cite{Ross:2008} \cite{Wu:2009} \cite{Perez02} \cite{Mei:2009} ) assume image
sequence to be blur free. But in reality, motion blur is inherent part of most
of the videos. Wu et al.\cite{Wu:2011} have developed BLUr-driven Tracker (BLUT)
framework for tracking motion-blurred targets. BLUT is based on the observation
that although motion blurs degrade the visual features of the target, they, at
thde same time, provide useful cues about the movements to help tracking.

BLUT framework successfully tracks blurred target when there is uniform motion
and the position of tracked object does not change drastically in successive
frames. But in our case, due to frequntly dropping of intermediate frame, this
criterion may not be satisfied.

@@

\section{Experimental Validation}
First, we have used synthetic images to test resilience to blur. We have scaled
down ARTag fiducial and our fiducial to size 150x150.  Then, we blurred both
fiducials along all orientations using different scales. Finally, we tried to
detect ARTag in these blurred images using ALVAR library\cite{alvar} and our fiducial
using algorithm given in previous section.

Our system has been tested on the image sequences captured from AR Drone
quadcopter. Each image sequence contains frames containing different fiducial
pattern. Sample output for each fiducial pattern is shown in Fig.
\ref{fig:output0} -- Fig. \ref{fig:output3}.
